---
title: "Creating a structured and reproducible project"
author: "Conor Neilson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a structured and reproducible project}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

## Justification

A most basic tenet of science is the idea that methods must be written so that anyone reading your work should be able to completely reproduce your project and get the same results. 

While this doctrine is generally accepted by all, in practise, this does not usually translate to having fully reproducible statistical analyses and code. Particularly in the life and physical sciences, where statistics is a necessity of the job rather than an area of interest, in can be difficult for the lone researcher or grad student to adopt best practises in code reproducibility.

While R is an excellent environment for statistics and data analysis, the reality is that for many academics and grad students outside of Computer Science, R is generally adopted during a period of high stress, where a thesis deadline is rapidly looming, and the only thought in the users mind is to **get that p-value**. Furthermore, a new user of R is faced with far more pressing challenges than writing clean code: setting a working directory, reading in data, how to write a model. The unfortunate end of this is that for many people, having reproducible analyses simply isn't a priority. 

However, tools to facilitate reproducible work are always appearing, and while many researchers find it difficult to prioritise reproducible code, they also understand that it is an important step in the workflow of research. 


## Primary differences

How its different - what its goals are



## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
